Nesta attacks study

### 2021-08-17 paperDraft/paperDraft.Rmd
theoretical part expanded - reactive vs pro-active moderation

# Section Abstract
This article describes an experimental intervention study based in a naturalistic, digital setting (Q&A forum - Reddit), utilizing a collective intelligence approach to content moderation and reduction of the level of verbal aggression among a selected group of Reddit users who regularly attack other community members. Collective Intelligence in this sense means exploring the collaboration between human and machine intelligence to develop solutions to social challenges. Artificial Intelligence was used to detect verbal aggression (personal attacks) and notify human volunteers about attacks. Volunteers after receiving notifications employed interventions based on norm or empathy promotion. We find that only those who were sanctioned with norms-inducing interventions had their personal attacks' user significantly decreased.

@@

# Automated versus Human-based Moderation
The hindrances and threats that go along with the Artificial Intelligence-based methods for moderation have been widely debated, with the most critical discussions revolving around technology performance (@macavaney2019hate, @schmidt2017survey). State-of-the-art solutions are mostly governed by statistical methods including deep learning and machine learning (@lecun2015deep, @sejnowski2020unreasonable, @jordan2015machine). Their performance is inherently tied to the amount of data being fed to the system and the quality of its annotation. At different stages of the process, from datasets gathering and preparation, annotation to the training or algorithms themselves, biases seem to be omnipresent (@binns2017like, @geva2019we @mehrabi2021survey). Users' of online services are also creative in their strategies to circumvent automated content moderation systems and as shown by @grondahl2018all, current techniques are vulnerable to the most common evasion attacks like word changes (inseting typos and leetspeak), word-boundary changes (inserting or removing whitespace), or word appending (appending common or non-hateful words like "love"). Generalisability of the models - an ability to perform well on datasets coming from sources other than the one used for training are an important shortcoming as well (@yin2021towards, @swamy2019studying, @rosa2019automatic). As shown by @wu2019errudite, @lipton2019troubling, and @musgrave2020metric in practice, creations of models often lacks thorough error analysis and legitimate experimental methodology, which can result in non-reproducibility. This is also connected with a potential lack of thorough understanding of the limitations of the models and spurious conclusions being made to a wider public. Specifically, @@lipton2019troubling distinguishes four dysfunctional patterns occurring in the current research paradigm in the industry and academia alike. First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second. Second, inability for successful identification of the sources of empirical gains (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect). Third, "mathiness" - the use obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon. Last but not least - misuse of language. This includes suggestive definitions without proper explanation of what they mean in the context (e.g. inflating good performance in simple NLP tasks to human-level natural understanding), overloading the papers with technical terminology, or suitcase words (those words that can encompass a variety of meanings, e.g. consciousness).

@@

At the same time, only automated methods can scan through the massive amount of content being generated every day on different platforms. On Facebook, there are more than 3B comments and likes daily (https://martech.org/facebook-3-2-billion-likes-comments-every-day/), 500M tweets are sent daily on Twitter (https://www.oberlo.com/blog/twitter-statistics), and over 2B comments made by users of Reddit in 2020 (https://old.reddit.com/r/blog/comments/k967mm/reddit_in_2020/) which is almost 3M comments made daily. With this amount of content, it's either impossible or extremely costly to scale the moderation workforce. One can also have doubts about the ethical aspects of hiring workers who are often unaware of how this kind of task will affect their well-being. Being submersed in the cyber-Augean stables takes a toll on many people. As examined by @roberts2014behind & @roberts2016commercial, workers who are hired for such tasks are often low-status and low-wage, isolated, and asked to keep what they've seen in secret under restrictive NDAs. Screening through the reported user-generated content is connected with exposure to violent and deeply disturbing materials, with child pornography, murders, or suicides as examples of the most extreme cases. This can lead to serious psychological damage, like depression, or PTSD (@roberts2014behind). Some of the employees filed a lawsuit against Facebook and as a result, the company agreed to pay $52M in compensation for mental health issues developed during the job (https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health).
Taking into consideration that Facebook employs 15K moderators (https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/?sh=6c6bdbbc54d0) and most likely more are needed to keep up with the growing amount of content, with the parallel considerations about the negative effects of content moderation on mental health, a collaboration between humans and machines in this area seems inevitable. There is yet another aspect here - what moderators deal with is mostly content reported by humans. And as shown in various studies and reports, a lot of children, teens or even adults do not report cyberbullying or harassment online (LINKS: https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945 ; https://www.adl.org/free-to-play-2020 ; https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf).

# Pro-active and reactive moderation

>>>>

# Section Abstract
This article describes an experimental intervention study based in a naturalistic, digital setting (Q&A forum - Reddit), utilizing a collective intelligence approach to content moderation and reduction of the level of verbal aggression among a selected group of Reddit users who regularly attack other community members. Collective Intelligence in this sense means exploring the collaboration between human and machine intelligence to develop solutions to social challenges. Artificial Intelligence was used to detect verbal aggression (personal attacks) and notify human volunteers about attacks. Volunteers after receiving notifications employed interventions based on norm or empathy promotion. We find that only those who were sanctioned with norms-inducing interventions had their personal attacks' level significantly decreased.

@@

# Automated versus Human-based Moderation
The hindrances and threats that go along with the Artificial Intelligence-based methods for moderation have been widely debated, with the most critical discussions revolving around technology performance (@macavaney2019hate, @schmidt2017survey). State-of-the-art solutions are mostly governed by statistical methods including deep learning and machine learning (@lecun2015deep, @sejnowski2020unreasonable, @jordan2015machine). Their performance is inherently tied to the amount of data being fed to the system and the quality of its annotation. At different stages of the process, from datasets gathering and preparation, annotation to the training or algorithms themselves, biases seem to be omnipresent (@binns2017like, @geva2019we @mehrabi2021survey). Users' of online services are also creative in their strategies to circumvent automated content moderation systems and as shown by @grondahl2018all, current techniques are vulnerable to the most common evasion attacks like word changes (inseting typos and leetspeak), word-boundary changes (inserting or removing whitespace), or word appending (appending common or non-hateful words like "love"). Lack of generalisability of the models - an ability to perform well on datasets coming from sources other than the one used for training is a serious shortcoming as well (@yin2021towards, @swamy2019studying, @rosa2019automatic). As shown by @wu2019errudite, @lipton2019troubling, and @musgrave2020metric in practice, creations of models often lacks thorough error analysis and legitimate experimental methodology, which can result in non-reproducibility. This is also connected with a potential lack of thorough understanding of the limitations of the models and spurious conclusions being made to a wider public. Specifically, @@lipton2019troubling distinguishes four dysfunctional patterns occurring in the current research paradigm in the industry and academia alike. First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second. Second, inability for successful identification of the sources of empirical gains (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect). Third, "mathiness" - the use obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon. Last but not least - misuse of language. This includes suggestive definitions without proper explanation of what they mean in the context (e.g. inflating good performance in simple NLP tasks to human-level understanding), overloading the papers with technical terminology, or suitcase words (those words that can encompass a variety of meanings, e.g. consciousness).

@@

At the same time, only automated methods can scan through the massive amount of content being generated every day on different platforms. On Facebook, there are more than 3B comments and likes daily (https://martech.org/facebook-3-2-billion-likes-comments-every-day/), 500M tweets are sent daily on Twitter (https://www.oberlo.com/blog/twitter-statistics), and over 2B comments made by users of Reddit in 2020 (https://old.reddit.com/r/blog/comments/k967mm/reddit_in_2020/) which is almost 3M comments made daily. With this amount of content, it's either impossible or extremely costly to scale the moderation workforce. One can also have doubts about the ethical aspects of hiring workers who are often unaware of how this kind of task will affect their well-being. Being submersed in the cyber-Augean stables takes a toll on many - as examined by @roberts2014behind & @roberts2016commercial, workers who are hired for such tasks are often low-status and low-wage, isolated, and asked to keep what they've seen in secret under restrictive NDAs. Screening through the reported user-generated content is connected with exposure to violent and deeply disturbing materials, with child pornography, murders, or suicides as examples of the most extreme cases. This can lead to serious psychological damage, like depression, or PTSD (@roberts2014behind). Some of the employees filed a lawsuit against Facebook and as a result, the company agreed to pay $52M in compensation for mental health issues developed during the job (https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health).
Taking into consideration that Facebook employs 15K moderators (https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/?sh=6c6bdbbc54d0) and most likely more are needed to keep up with the growing amount of content, with the parallel considerations about the negative effects of content moderation on mental health, a collaboration between humans and machines in this area seems inevitable.

# Pro-active and reactive moderation
There are different approaches when it comes to the moderation of online content. One can follow the workflow of reactive moderation, which happens once the content is published. Harmful messages can be either reported by the users of the platforms or automated methods and then sent for review to moderators. A set of actions can be then taken depending on the platform and their community guidelines - on the content or user level. A harmful message can be deleted, made invisible to other users, or certain profanities can be altered with special signs to censor them. Depending on the type and amount of infraction, a particular user can be warned, muted or shadowbanned, or banned from further participation in the community for a period of time. The weakness of the reactive method is that the damage is done. Whoever is the recipient of the abusive message has the chance to see it and potentially suffer (@hoff2009cyberbullying, @keipi2016online, Wwachs2019associations). 
Yet another weakness connected with relying solely on human reports is the content that is harmful but unreported by a receipted or any bystander. Although the exact scale of unreported content is not known, various self-report studies show that a lot of children, teens, or even adults do not report cyberbullying or harassment online (LINKS: https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945 ; https://www.adl.org/free-to-play-2020 ; https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf).

Yet another type of moderation can be distinguished as pro-active or pre-moderation. In pre-moderation, automated methods are either based on Artificial Intelligence or other less sophisticated tools (e.g. blacklists) and can screen the content before it gets published. If a type of harmful message gets detected, it can be removed before reaching the recipient. Due to the aforementioned dubious performance of state-of-the-art statistical methods, particularly low precision, they are rarely used autonomously.

Pro-active moderation can be utilized using AI or other methods to promote socially positive engagement. Instead of or in the combination with punitive solutions like privileges restriction, one can induce empathy or community norms with counter-speech. Counter speech as described by Dangerous Speech Project (https://dangerousspeech.org/counterspeech/) is "any direct response to hateful or harmful speech which seeks to undermine it". As examined by @munger2017tweetment, counter-speech can be effective in the reduction of racist tweets (although only in the condition in which a white male with high followers was approaching another white male). In a study conducted by @bilewicz2021artificial, a bot 
...

### 2021-08-17 paperDraft/paperDraft.tex
theoretical part expanded - reactive vs pro-active moderation

This article describes an experimental intervention study based in a
naturalistic, digital setting (Q\&A forum - Reddit), utilizing a
collective intelligence approach to content moderation and reduction of
the level of verbal aggression among a selected group of Reddit users
who regularly attack other community members. Collective Intelligence in
this sense means exploring the collaboration between human and machine
intelligence to develop solutions to social challenges. Artificial
Intelligence was used to detect verbal aggression (personal attacks) and
notify human volunteers about attacks. Volunteers after receiving
notifications employed interventions based on norm or empathy promotion.
We find that only those who were sanctioned with norms-inducing
interventions had their personal attacks' user significantly decreased.

@@

The hindrances and threats that go along with the Artificial
Intelligence-based methods for moderation have been widely debated, with
the most critical discussions revolving around technology performance
(MacAvaney et al. (2019), Schmidt \& Wiegand (2017)). State-of-the-art
solutions are mostly governed by statistical methods including deep
learning and machine learning (LeCun, Bengio, \& Hinton (2015),
Sejnowski (2020), Jordan \& Mitchell (2015)). Their performance is
inherently tied to the amount of data being fed to the system and the
quality of its annotation. At different stages of the process, from
datasets gathering and preparation, annotation to the training or
algorithms themselves, biases seem to be omnipresent (Binns, Veale, Van
Kleek, \& Shadbolt (2017), Geva, Goldberg, \& Berant (2019) Mehrabi,
Morstatter, Saxena, Lerman, \& Galstyan (2021)). Users' of online
services are also creative in their strategies to circumvent automated
content moderation systems and as shown by Gröndahl, Pajola, Juuti,
Conti, \& Asokan (2018), current techniques are vulnerable to the most
common evasion attacks like word changes (inseting typos and leetspeak),
word-boundary changes (inserting or removing whitespace), or word
appending (appending common or non-hateful words like ``love'').
Generalisability of the models - an ability to perform well on datasets
coming from sources other than the one used for training are an
important shortcoming as well (Yin \& Zubiaga (2021), Swamy, Jamatia, \&
Gambäck (2019), Rosa et al. (2019)). As shown by Wu, Ribeiro, Heer, \&
Weld (2019), Lipton \& Steinhardt (2019), and Musgrave, Belongie, \& Lim
(2020) in practice, creations of models often lacks thorough error
analysis and legitimate experimental methodology, which can result in
non-reproducibility. This is also connected with a potential lack of
thorough understanding of the limitations of the models and spurious
conclusions being made to a wider public. Specifically, @Lipton \&
Steinhardt (2019) distinguishes four dysfunctional patterns occurring in
the current research paradigm in the industry and academia alike. First,
the inability to draw a clear distinction between speculation and
explanation, with the first one often being disguised as the second.
Second, inability for successful identification of the sources of
empirical gains (whether it was problem formulation, optimization of the
heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet
another aspect). Third, ``mathiness'' - the use obscure language and
often covering weak argumentation with the alluring but often apparent
depth of technical jargon. Last but not least - misuse of language. This
includes suggestive definitions without proper explanation of what they
mean in the context (e.g.~inflating good performance in simple NLP tasks
to human-level natural understanding), overloading the papers with
technical terminology, or suitcase words (those words that can encompass
a variety of meanings, e.g.~consciousness).

@@

At the same time, only automated methods can scan through the massive
amount of content being generated every day on different platforms. On
Facebook, there are more than 3B comments and likes daily
(\url{https://martech.org/facebook-3-2-billion-likes-comments-every-day/}),
500M tweets are sent daily on Twitter
(\url{https://www.oberlo.com/blog/twitter-statistics}), and over 2B
comments made by users of Reddit in 2020
(\url{https://old.reddit.com/r/blog/comments/k967mm/reddit_in_2020/})
which is almost 3M comments made daily. With this amount of content,
it's either impossible or extremely costly to scale the moderation
workforce. One can also have doubts about the ethical aspects of hiring
workers who are often unaware of how this kind of task will affect their
well-being. Being submersed in the cyber-Augean stables takes a toll on
many people. As examined by Roberts (2014) \& Roberts (2016), workers
who are hired for such tasks are often low-status and low-wage,
isolated, and asked to keep what they've seen in secret under
restrictive NDAs. Screening through the reported user-generated content
is connected with exposure to violent and deeply disturbing materials,
with child pornography, murders, or suicides as examples of the most
extreme cases. This can lead to serious psychological damage, like
depression, or PTSD (Roberts (2014)). Some of the employees filed a
lawsuit against Facebook and as a result, the company agreed to pay
\$52M in compensation for mental health issues developed during the job
(\url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}).
Taking into consideration that Facebook employs 15K moderators
(\url{https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/?sh=6c6bdbbc54d0})
and most likely more are needed to keep up with the growing amount of
content, with the parallel considerations about the negative effects of
content moderation on mental health, a collaboration between humans and
machines in this area seems inevitable. There is yet another aspect here
- what moderators deal with is mostly content reported by humans. And as
shown in various studies and reports, a lot of children, teens or even
adults do not report cyberbullying or harassment online (LINKS:
\url{https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945}
; \url{https://www.adl.org/free-to-play-2020} ;
\url{https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf}).

@@

@@

@@

@@

@@

>>>>

This article describes an experimental intervention study based in a
naturalistic, digital setting (Q\&A forum - Reddit), utilizing a
collective intelligence approach to content moderation and reduction of
the level of verbal aggression among a selected group of Reddit users
who regularly attack other community members. Collective Intelligence in
this sense means exploring the collaboration between human and machine
intelligence to develop solutions to social challenges. Artificial
Intelligence was used to detect verbal aggression (personal attacks) and
notify human volunteers about attacks. Volunteers after receiving
notifications employed interventions based on norm or empathy promotion.
We find that only those who were sanctioned with norms-inducing
interventions had their personal attacks' level significantly decreased.

@@

The hindrances and threats that go along with the Artificial
Intelligence-based methods for moderation have been widely debated, with
the most critical discussions revolving around technology performance
(MacAvaney et al. (2019), Schmidt \& Wiegand (2017)). State-of-the-art
solutions are mostly governed by statistical methods including deep
learning and machine learning (LeCun, Bengio, \& Hinton (2015),
Sejnowski (2020), Jordan \& Mitchell (2015)). Their performance is
inherently tied to the amount of data being fed to the system and the
quality of its annotation. At different stages of the process, from
datasets gathering and preparation, annotation to the training or
algorithms themselves, biases seem to be omnipresent (Binns, Veale, Van
Kleek, \& Shadbolt (2017), Geva, Goldberg, \& Berant (2019) Mehrabi,
Morstatter, Saxena, Lerman, \& Galstyan (2021)). Users' of online
services are also creative in their strategies to circumvent automated
content moderation systems and as shown by Gröndahl, Pajola, Juuti,
Conti, \& Asokan (2018), current techniques are vulnerable to the most
common evasion attacks like word changes (inseting typos and leetspeak),
word-boundary changes (inserting or removing whitespace), or word
appending (appending common or non-hateful words like ``love''). Lack of
generalisability of the models - an ability to perform well on datasets
coming from sources other than the one used for training is a serious
shortcoming as well (Yin \& Zubiaga (2021), Swamy, Jamatia, \& Gambäck
(2019), Rosa et al. (2019)). As shown by Wu, Ribeiro, Heer, \& Weld
(2019), Lipton \& Steinhardt (2019), and Musgrave, Belongie, \& Lim
(2020) in practice, creations of models often lacks thorough error
analysis and legitimate experimental methodology, which can result in
non-reproducibility. This is also connected with a potential lack of
thorough understanding of the limitations of the models and spurious
conclusions being made to a wider public. Specifically, @Lipton \&
Steinhardt (2019) distinguishes four dysfunctional patterns occurring in
the current research paradigm in the industry and academia alike. First,
the inability to draw a clear distinction between speculation and
explanation, with the first one often being disguised as the second.
Second, inability for successful identification of the sources of
empirical gains (whether it was problem formulation, optimization of the
heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet
another aspect). Third, ``mathiness'' - the use obscure language and
often covering weak argumentation with the alluring but often apparent
depth of technical jargon. Last but not least - misuse of language. This
includes suggestive definitions without proper explanation of what they
mean in the context (e.g.~inflating good performance in simple NLP tasks
to human-level understanding), overloading the papers with technical
terminology, or suitcase words (those words that can encompass a variety
of meanings, e.g.~consciousness).

@@

At the same time, only automated methods can scan through the massive
amount of content being generated every day on different platforms. On
Facebook, there are more than 3B comments and likes daily
(\url{https://martech.org/facebook-3-2-billion-likes-comments-every-day/}),
500M tweets are sent daily on Twitter
(\url{https://www.oberlo.com/blog/twitter-statistics}), and over 2B
comments made by users of Reddit in 2020
(\url{https://old.reddit.com/r/blog/comments/k967mm/reddit_in_2020/})
which is almost 3M comments made daily. With this amount of content,
it's either impossible or extremely costly to scale the moderation
workforce. One can also have doubts about the ethical aspects of hiring
workers who are often unaware of how this kind of task will affect their
well-being. Being submersed in the cyber-Augean stables takes a toll on
many - as examined by Roberts (2014) \& Roberts (2016), workers who are
hired for such tasks are often low-status and low-wage, isolated, and
asked to keep what they've seen in secret under restrictive NDAs.
Screening through the reported user-generated content is connected with
exposure to violent and deeply disturbing materials, with child
pornography, murders, or suicides as examples of the most extreme cases.
This can lead to serious psychological damage, like depression, or PTSD
(Roberts (2014)). Some of the employees filed a lawsuit against Facebook
and as a result, the company agreed to pay \$52M in compensation for
mental health issues developed during the job
(\url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}).
Taking into consideration that Facebook employs 15K moderators
(\url{https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/?sh=6c6bdbbc54d0})
and most likely more are needed to keep up with the growing amount of
content, with the parallel considerations about the negative effects of
content moderation on mental health, a collaboration between humans and
machines in this area seems inevitable.

@@

There are different approaches when it comes to the moderation of online
content. One can follow the workflow of reactive moderation, which
happens once the content is published. Harmful messages can be either
reported by the users of the platforms or automated methods and then
sent for review to moderators. A set of actions can be then taken
depending on the platform and their community guidelines - on the
content or user level. A harmful message can be deleted, made invisible
to other users, or certain profanities can be altered with special signs
to censor them. Depending on the type and amount of infraction, a
particular user can be warned, muted or shadowbanned, or banned from
further participation in the community for a period of time. The
weakness of the reactive method is that the damage is done. Whoever is
the recipient of the abusive message has the chance to see it and
potentially suffer (Hoff \& Mitchell (2009), Keipi, Näsi, Oksanen, \&
Räsänen (2016), Wwachs2019associations). Yet another weakness connected
with relying solely on human reports is the content that is harmful but
unreported by a receipted or any bystander. Although the exact scale of
unreported content is not known, various self-report studies show that a
lot of children, teens, or even adults do not report cyberbullying or
harassment online (LINKS:
\url{https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945}
; \url{https://www.adl.org/free-to-play-2020} ;
\url{https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf}).

Yet another type of moderation can be distinguished as pro-active or
pre-moderation. In pre-moderation, automated methods are either based on
Artificial Intelligence or other less sophisticated tools
(e.g.~blacklists) and can screen the content before it gets published.
If a type of harmful message gets detected, it can be removed before
reaching the recipient. Due to the aforementioned dubious performance of
state-of-the-art statistical methods, particularly low precision, they
are rarely used autonomously.

Pro-active moderation can be utilized using AI or other methods to
promote socially positive engagement. Instead of or in the combination
with punitive solutions like privileges restriction, one can induce
empathy or community norms with counter-speech. Counter speech as
described by Dangerous Speech Project
(\url{https://dangerousspeech.org/counterspeech/}) is ``any direct
response to hateful or harmful speech which seeks to undermine it.'' As
examined by Munger (2017), counter-speech can be effective in the
reduction of racist tweets (although only in the condition in which a
white male with high followers was approaching another white male). In a
study conducted by Bilewicz et al. (2021), a bot \ldots{}

@@

\leavevmode\hypertarget{ref-bilewicz2021artificial}{}%
Bilewicz, M., Tempska, P., Leliwa, G., Dowgiałło, M., Tańska, M.,
Urbaniak, R., \& Wroczyński, M. (2021). Artificial intelligence against
hate: Intervention reducing verbal aggression in the social network
environment. \emph{Aggressive Behavior}, \emph{47}(3), 260--266.

@@

\leavevmode\hypertarget{ref-hoff2009cyberbullying}{}%
Hoff, D. L., \& Mitchell, S. N. (2009). Cyberbullying: Causes, effects,
and remedies. \emph{Journal of Educational Administration}.

@@

\leavevmode\hypertarget{ref-keipi2016online}{}%
Keipi, T., Näsi, M., Oksanen, A., \& Räsänen, P. (2016). \emph{Online
hate and harmful content: Cross-national perspectives}. Taylor \&
Francis.

@@

\leavevmode\hypertarget{ref-munger2017tweetment}{}%
Munger, K. (2017). Tweetment effects on the tweeted: Experimentally
reducing racist harassment. \emph{Political Behavior}, \emph{39}(3),
629--649.
